--- 
title: "Landscape Ecology and GIS"
author: "Andres Hernandez M.Sc"
date: "`r Sys.Date()`"
bibliography:
- book.bib
- packages.bib
description: This is a minimal example of using the bookdown package to write a book.
  The output format for this example is bookdown::gitbook.
documentclass: book
link-citations: yes
site: bookdown::bookdown_site
biblio-style: apalike
---

```{r, include=FALSE}
library(knitr)
library(dplyr)
library(kableExtra)
```

```{r eval=FALSE, include=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


# Syllabus {-}

## Contact information {-}

```{r echo=FALSE, results='asis', warning=FALSE,out.width='100%'}
prof <- data.frame(Instructor = '![](https://scholar.google.com/citations?view_op=view_photo&user=zMoJ8n4AAAAJ&citpid=7)',Info="Dr. Diego F. Cuadros. Assistant Professor of Health Geography and Disease Modeling, University of Cincinnati. **Office:** 401 C Braunstein Hall, Main Campus. **Email:** diego.cuadros@uc.edu")
# kable(, caption = "Book",col.names = "")
kable(prof) %>%
  kable_styling(full_width = F,position = "left") %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, width = "30em")
```


## Content {-}

The goal of this course is to exemplify the role of ArcGIS in analysis of spatial data in landscape ecology applications. At the beginning, we will review the fundamentals of the use of ArcMap interface, basic file structures and operations. Then, we will explore the capabilities of manipulating information in ArcGIS, and finally the use of ArcGIS in real world scenarios.

* Format of the Lab sessions:
    + This is a class about the use of ArcGIS in landscape ecology related problems
    + Videos with detailed explanation about the topics.

* Lab sessions tutorials and materials can be found [here!!!](https://andher1802.github.io/landscapegis/)

